First we must load the **tidyverse**
```{r, message = FALSE, echo = TRUE}
library("tidyverse")
```

## Question 1 - Cocktails!

We've put together a small list containing the ingredients of some classic cocktails
```{r, echo = TRUE}
data(cocktails, package = "jrTidyverse2")
```

a) How many cocktails are in the list? 
    ```{r}
    str(cocktails)
    ```

b) Create a tibble called `drinks`, where one column contains the name of the cocktail, and the other column contains the vector of ingredients
    ```{r}
    drinks = tibble(cocktail = names(cocktails),
                    ingredients = cocktails)
    ```
    
c) Create a new column that contains the number of ingredients in each column using `mutate()` and **purrr**
    ```{r}
    drinks = drinks %>% 
      mutate(total_ingredients = map(ingredients, length))
    ```
    
d) We're off out! Tonight we're particularly thirsty for a cocktail with rum in it. Filter `drinks` such that it only has cocktails containing rum
    ```{r}
    drinks %>%
      mutate(contains_rum = map_lgl(ingredients,
                                    ~ any(.x == "rum"))) %>%
      filter(contains_rum)
    ```
    
## Question 2 - Monthly data
