First we must load the **tidyverse**
```{r, message = FALSE, echo = TRUE}
library("tidyverse")
```

## Question 1 - Cocktails!

We've put together a small list containing the ingredients of some classic cocktails
```{r, echo = TRUE}
data(cocktails, package = "jrTidyverse2")
```

a) How many cocktails are in the list? 
    ```{r}
    str(cocktails)
    ```

b) Create a tibble called `drinks`, where one column contains the name of the cocktail, and the other column contains the vector of ingredients
    ```{r}
    drinks = tibble(cocktail = names(cocktails),
                    ingredients = cocktails)
    ```
    
c) Create a new column that contains the number of ingredients in each column using `mutate()` and **purrr**
    ```{r}
    drinks = drinks %>% 
      mutate(total_ingredients = map(ingredients, length))
    ```
    
d) We're off out! Tonight we're particularly thirsty for a cocktail with rum in it. Filter `drinks` such that it only has cocktails containing rum
    ```{r}
    drinks %>%
      mutate(contains_rum = map_lgl(ingredients,
                                    ~ any(.x == "rum"))) %>%
      filter(contains_rum)
    ```
    
## Question 2 - Beer !

So, we're at the pub with 8 mates and it's your round. In total you've been tasked with ordering 4 ales, 3 ipas, 1 stout plus an ale for yourself! We can load a data set of all of the ale, ipa and stouts that the pub sells from the course package
```{r}
(data(beer_tidy, package = "jrTidyverse2"))
```

We're going to randomly select each persons drink using **purrr**. If people had asked for an even number of ales, ipas and stouts we could have done this without **purrr** like so
```{r}
beer_tidy %>% 
  group_by(Type) %>% 
  sample_n(3)
```

a) Nest the data according to the drink `Type` and save it as `pub`.
    ```{r}
    pub = beer_tidy %>% 
      nest(-Type)
    ```

b) Create a column called `n` that contains the total number of each drink `Type` you need to order
    ```{r}
    pub = pub %>% 
      mutate(n = c(5, 3, 1))
    ```

c) Create a new column called order that contains the randomly sampled drinks you are going to order. You should be using `map2()` to parallel map over the columns `data` and `n`. You should also be using `sample_n()` to perform the sampling.
    ```{r}
    pub = pub %>% 
      mutate(order = map2(data, n, sample_n))
    # or 
    # mutate(order = map2(.x = data, .y = n, ~sample_n(.x, .y)))
    ```
    
d) To see the drinks, select only the `Type` and `order` column, then `unnest()`
    ```{r}
    pub %>% 
      select(Type, order) %>% 
      unnest()
    ```


## Question 3 - Happiness

You may remember the happiness data we used for practical 1 was recorded over 3 years; 2015, 2016 and 2017. For this question I've turned the happiness list in 3 tibbles, with each one representing the year. Running the following code will copy each file into your current working directory as a `.csv` file
```{r, echo = TRUE, results='hide'}
library("jrTidyverse2")
get_happiness()
```

a) Using a combination of **purrr** and the `unnest()` function from **tidyr**, read in and combine the 3 data sets. Don't delete the column containing the file name!
    ```{r, message = FALSE, warning = FALSE}
    fnames = list.files("happiness", recursive = TRUE, full.names = TRUE)
    happiness = tibble(fname = fnames) %>%
      mutate(data = map(fnames, read_csv)) %>% 
      unnest()
    ```
    ```{r, echo = FALSE, results='hide', message = FALSE, warning = FALSE}
    file.remove(fnames)
    file.remove("happiness/")
    ```

b) The data within the csv files doesn't contain the year. Fortunately the file name does! Use the column containing the filename to create a column called `Year`. Have a look at the `str_remove()` or `parse_number()` functions from **stringr** and **readr** respectively
    ```{r}
    happiness = happiness %>% 
      mutate(Year = parse_number(fname)) %>% 
      select(-fname)
    # or
    # happiness = happiness %>%
    #   mutate(Year = str_remove(fname, ".csv"),
    #          Year = as.numeric(Year)) %>%
    #   select(-fname)
    ```

c) Pick 3 countries and plot their happiness rank over time. 
    ```{r}
    happiness %>% 
      filter(Country %in% c("Denmark", "United Kingdom", "United States")) %>% 
      ggplot(aes(x = Year, y = `Happiness Rank`, colour = Country)) + 
      geom_line() + 
      geom_point()
    ```

d) Every country in the data set has requested that they have their data sent to them individually. Make use of  **purrr**'s parallel mapping functions and `nest()` to write the data to `.csv` files
    ```{r, eval = FALSE}
    happiness_nest = happiness %>% 
      nest(-Country)
    map2(happiness_nest$Country, happiness_nest$data, 
         ~write_csv(.y, path = paste0(.x, ".csv"))
    ```
